Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains

### 2014-12-12 paper_new.tex
all files are added
structure is updated finally

%%%%%%%%%%%%%%% Structure of paper %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% abstract
% introduction
% high level action definition
% low level action definition
% action execution
%	full action definition
% features
% results
% conclusion
%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{color}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{Mohamad Javad Aein         \and
        Eren Erdal Aksoy         \and
        Florentin Woergoetter %etc.
}

@@

\institute{M. J. Aein \at
              Friedrich-Hund Platz 1, 37077 Goettingen,  Germany\\
              Tel.: +49-551-3910766\\
              Fax: +49-551-3910769\\
              \email{maein@gwdg.de}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           E. E. Aksoy \at
              Friedrich-Hund Platz 1, 37077 Goettingen,  Germany
           \and
           F. Woergoetter \at
              Friedrich-Hund Platz 1, 37077 Goettingen,  Germany
}

@@

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper a new implementation of the library of actions is presented.
Library of actions is a software application which implements  manipulation actions on robotic systems using the semantic event chain framework.
A general definition for manipulation actions is presented which contains both in symbolic and sub-symbolic components.
To connect these two domains, a finite state machine is presented to execute manipulation actions.
The actions are performed both individually and chained sequentially to perform more complex scenarios.
This opens the possibility to use higher-level planners that work in symbolic domain.
The results show that the proposed methodology and software are capable of performing useful human-like actions.

\keywords{library of actions \and manipulation actions \and semantic event chains \and }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{intro}

% It remains largely a puzzle how action knowledge can be efficiently structured for robotics applications.
% In a recent paper \cite{TAMD13}, we had discussed that human manipulation actions can be captured by a limited ontology-tree
% and we had argued that there is only a quite small number of basic actions existing (less than 30), which cover most if not all of our uni-manual manipulations.
% 
% This, we believe, offers the unique opportunity to structure the robot's manipulation action-space
% by defining all these actions in a default way to also store them in an action library.
% For any given robot (with not too different embodiment) execution of an action then means to access the required library function
% only having to re-parameterize it with respect to the {\em specific} action-situation (the scene) also taking into account all embodiment-specific constraints.
% 
% This idea as such is quite straight-forward but requires addressing many difficult problems.
% First and foremost we are asking for an appropriate action-representation from which an action library could be formed.
% Second, we need to define an architecture that can be used to access the library and actually execute an action.
% % \begin{figure}
% % % Use the relevant command to insert your figure file.
% % % For example, with the graphicx package use
% %   \includegraphics{example.eps}
% % % figure caption is below the figure
% % \caption{Please write your figure caption here}
% % \label{fig:1}       % Give a unique label
% % \end{figure}
% \begin{figure}
%       \centering
%       \includegraphics[scale=0.6]{./pdf/overview.pdf}
%       \caption{An action is defined and executed using three levels.}
%       \label{fig:overview}
% \end{figure}

% To address both problems in a conjoint, process-oriented way, we suggest to use a layered action representation,
% which defines an action going from "generic" to "specific".
% We start at the top-level (Fig. \ref{fig:overview}, top) with a symbolic definition of actions proposed in \cite{Aksoy11}
% by which uni-manual human manipulations are defined as sequences of graphs that show how relations between objects change in the course of an action.
% From this a matrix representation of those graph sequences, called Semantic Event Chain (SEC), can be derived by which "the essence" of an action
% -- the sequence of changes in a scene resulting from the action -- is encoded .
% At this top-level objects and other action relevant parameters are encoded only in a very abstract way (described in Section \ref{sec:high-level} below).
% 
% One level down we define a finite state machine, which receives inputs from the SECs and produces an execution protocol of so-called "action primitives"
% (Fig. \ref{fig:overview}, middle).
% In general all robot arm- and hand-systems have low-level controllers, which make it possible to implement such action primitives.
% These low-level primitives are described in detail in Section~\ref{section_primitives}.
% Here the interfacing to the real world -- to the currently observed situation -- takes place
% and the {\em actual} execution parameters are determined from sensor information at the bottom level (Fig. \ref{fig:overview}, bottom).
% We use position and force sensors at the robot arm, a vision system to observe the scene, and tactile sensors of the robot hand.
% 
% By this, we achieve a systematic and general way of representing and executing all the actions of the ontology, which together form a \emph{library} of human-like manipulations.
% % This library can then be used by a higher level task planner to perform more complex action sequences (for an example see Section \ref{subsection:scenario}).
% 
% The proposed methodology and the resulting library of actions have some advantageous features.
% First there is the ability to perform actions on any robot manipulator platform that provides the required low-level primitive and sensor information.
% Second the framework generalizes well to different actions, objects and situations.
% Third, it provides the necessary actions with pre- and post-conditions for a higher level planner to perform more complex tasks.
% Finally, it provides mechanisms to detect failures during execution and allows reacting to them.

@@

% Next follows Section \ref{subsection:stateoftheart} on the state of the art.
% Then, in Section~\ref{section:framework} the proposed methodology is described.
% Section ~\ref{section:fault} is on failure detection and handling.
% In Section~\ref{section:experiments} we present the results of experiments performed on our robotic setup.
% Finally, Section \ref{section:conclusion} provides a conclusion of the paper.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{High-level Action Definition}
\label{sec:high-level}
In this section we give a high-level definition of manipulation actions.
At this level, definitions are mainly symbolic, abstract and close to human description.

@@

% \subsection{Mid-level Sequencer}
% \label{sec:mid-level}
% 
% % In fig.\ref{fig:overview}, a three-layer structure is proposed to implement actions.
% In this section we introduce the middle layer of fig.\ref{fig:overview}.
% The middle layer is a sequencer which relates the high-level components to the low-level hardware.
% This sequencer is realized by using a finite state machine.
% This state machine follows the high-level action definition,
% creates a sequence of primitives and sends them to the proper component at the low-level.
% On the other hand, it receives the real object relations from the low-level, and uses them to make state transitions.
% 
% An FSM is a logic unit, that determines outputs and the next state of a system, based on the current state and inputs.
% It is formally defined as a 6-tuple $(S,U,Y,f_1,f_2,s_1)$.
% 
% The following paragraphs show the definition of these variables.
% It is also shown how these variables are related to the high-level and low-level components.
% In particular, the variables for the put-on example are derived to complete the example.
% For the put-on action the resulting FSM is depicted in Fig. \ref{fig:sec_fsm}.
% 
% \subsubsection{States ($S$)}
% As the name suggests, there exists a finite set of states in an FSM denoted by $S$.
% The interpretation of these states depends on the application.
% In our application, each column of SEC matrix shows a state of the system.
% Therefore, states of FSM are associated with the columns of a SEC.
% For example, the SEC matrix for put-on has five columns, therefore the FSM has five states : $S=\{S(1), S(2)\cdots ,S(5)\}$ as shown in Fig. \ref{fig:action_graph_sec}.
% 
% \subsubsection{Inputs ($U$)}
% The inputs of the FSM, are the inputs of the system.
% In action execution, the inputs are the real relations.
% There are six real relations, therefore we need six inputs $U=[U(1),U(2), \cdots ,U(6)]^T$.
% For the put-on example, the inputs are highlighted in Fig. \ref{fig:action_graph_sec}.
% 
% \subsubsection{Outputs ($Y$)}
% An FSM can produce outputs depending on current state and inputs.
% % These outputs are defined in terms of defined commands of the application.
% In our application, the outputs are a combination of arm/hand primitives, that should get called in the appropriate sequence.
% In the put-on example there are five states, therefore there are five outputs $Y=\{Y(1), Y(2)\cdots ,Y(5)\}$,
% shown in Fig. \ref{fig:action_graph_sec}.
% Since the last state is the goal state, the last output is always empty.
% 
% \subsubsection{State transition function ($f_1$)}
% The state transition function determines the next state, based on current state and inputs.
% 
% In action execution, the transition from state $i$ to $i+1$ happens when the inputs are equal to the $(i+1)$th column of the SEC matrix.
% When checking the equality, the inputs that correspond to don't-care relations are not taken into account.
% Hence, the transition function for put-on example is as follows:
% \begin{equation}
% \label{eq:f_1_action}
%  \underset{i=1,2,3,4}{f_1(S(i),U)}=\left\{\begin{matrix}
% S(i+1) & \text{if}\,\, U=SEC(:,i+1)\\
% S(i) & otherwise
% \end{matrix}\right.
% \end{equation}
% 
% \subsubsection{Output function ($f_2$)}
% 
% In general, the outputs of an FSM depend on state and inputs.
% However, here we use a specific kind of FSM called Moore machine, in which outputs depend only on the states.
% Hence we have a simple output function which associates outputs to each state:
% \begin{equation}
% \label{eq:f_2}
%  \underset{i=1,2,3,4}{f_2(S(i))}= Y(i)
% \end{equation}
% 
% \subsubsection{Initial state ($S(1)$)}
% The initial state is associated with the first columns of the SEC that represents the initial relations between objects.
% It is verified at the beginning of the action that the real relations match the first column of the SEC matrix, otherwise the action won't start.

@@

\subsection{Software}
\label{sec:software}
The library of actions is implemented as an application in the Open Robot Control Software (Orocos) framework \cite{rtt-url,soetens2006}.
The Orocos is a framework to develop real-time robotic and automation applications.
In a typical Orocos application, several components exist which communicate over (possibly real-time) data ports.
The library of actions consists of several components which are shown in fig.\ref{fig:aladdin_structure}.
Some of the components communicate to hardware (Sensors and actuators), while others perform calculations and control the execution of actions.
The components are described in the following:
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/aladdin_structure.pdf}
      \caption{ Block diagram of the software for action library.
      The interconnection of the components are shown as well as the interface to ROS nodes and hardware.
}
      \label{fig:aladdin_structure}
\end{figure*}

@@

% \subsection{Experiments}
% \label{sec:experiments}
% \subsection{Discussion}
% \label{sec:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

% \paragraph{Paragraph headings} Use paragraph headings as needed.
% \begin{equation}
% a^2+b^2=c^2
% \end{equation}

% % % % For one-column wide figures use
% % % \begin{figure}
% % % % Use the relevant command to insert your figure file.
% % % % For example, with the graphicx package use
% % %   \includegraphics{example.eps}
% % % % figure caption is below the figure
% % % \caption{Please write your figure caption here}
% % % \label{fig:1}       % Give a unique label
% % % \end{figure}
%
% % % % For two-column wide figures use
% % % \begin{figure*}
% % % % Use the relevant command to insert your figure file.
% % % % For example, with the graphicx package use
% % %   \includegraphics[width=0.75\textwidth]{example.eps}
% % % % figure caption is below the figure
% % % \caption{Please write your figure caption here}
% % % \label{fig:2}       % Give a unique label
% % % \end{figure*}
%
% For tables use
% % % % \begin{table}
% % % % % table caption is above the table
% % % % \caption{Please write your table caption here}
% % % % \label{tab:1}       % Give a unique label
% % % % % For LaTeX tables use
% % % % \begin{tabular}{lll}
% % % % \hline\noalign{\smallskip}
% % % % first & second & third  \\
% % % % \noalign{\smallskip}\hline\noalign{\smallskip}
% % % % number & number & number \\
% % % % number & number & number \\
% % % % \noalign{\smallskip}\hline
% % % % \end{tabular}
% % % % \end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{actionlib_journal}   % name your BibTeX data base

% Non-BibTeX users please use
% % \begin{thebibliography}{}
% % %
% % % and use \bibitem to create references. Consult the Instructions
% % % for authors for reference list style.
% % %
% % \bibitem{RefJ}
% % % Format for Journal Reference
% % Author, Article title, Journal, Volume, page numbers (year)
% % % Format for books
% % \bibitem{RefB}
% % Author, Book title, page numbers. Publisher, place (year)
% % % etc
% % \end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
%% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%%!PS-Adobe-3.0 EPSF-3.0
%%%BoundingBox: 19 19 221 221
%%%CreationDate: Mon Sep 29 1997
%%%Creator: programmed by hand (JK)
%%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url} 
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
%\usepackage{slashbox}
%\usepackage{multicol}
\usepackage{xspace}

\usepackage{natbib}

\usepackage{lineno,hyperref}

\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\newcommand{\mathkomma}{\quad ,}
\newcommand{\mathpunkt}{\quad .}
\newcommand{\Real}{{\mathbb R}}

\def\etc{etc.\@\xspace}
\def\eg{e.g.\@\xspace}
\def\ie{i.e.\@\xspace}

\newcommand{\red}[1]{\textcolor{red}{#1}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document} \sloppy

\title{Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{  Mohamad Javad Aein      \and  	 Florentin  W\"org\"otter	 \and  Eren Erdal Aksoy  	 }

@@

\institute{   M. J. Aein,  		F.~W\"org\"otter , E.~E.~Aksoy  \at
              Georg-August-Universit\"at G\"ottingen, BCCN, \\Department for Computational Neuroscience,
              Inst. Physics-3 \\ Friedrich-Hund Platz 1, D-37077 G{\"o}ttingen, Germany \\
              \email{[maein,worgott,eaksoy]@gwdg.de}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
%           \and
%           S. Author \at
%              second address
}

@@

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In this paper a new implementation of the library of actions is presented.
Library of actions is a software application which implements  manipulation actions on robotic systems using the semantic event chain framework.
A general definition for manipulation actions is presented which contains both in symbolic and sub-symbolic components.
To connect these two domains, a finite state machine is presented to execute manipulation actions.
The actions are performed both individually and chained sequentially to perform more complex scenarios.
This opens the possibility to use higher-level planners that work in symbolic domain.
The results show that the proposed methodology and software are capable of performing useful human-like actions.

\keywords{Library of Actions \and Execution \and Manipulation Action \and  Semantic Event Chain}

% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Humans are  ..

The rest of the paper is organized as follows. We start with introducing the state of the art. We then continue with a detailed description of each processing step. Next, we provide experimental results on various datasets and finally we finish with a discussion.

@@

%\newpage  %% needed for single columns
%\clearpage  %% needed for two columns
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State of the Art}
\label{sec:soa}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}
\label{sec:method}

Before describing the complete framework in detail, we will briefly provide an overview of each algorithmic step illustrated in Fig.~\ref{fig:block_diagram}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Manipulation Observation}
\label{sec:observation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Segmentation and Tracking}
\label{sec:segmentationandtracking}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semantic Event Chain (SEC) Extraction}
\label{sec:secs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning of Model SECs}
\label{sec:learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{High-level Action Definition}
\label{sec:high-level}
In this section we give a high-level definition of manipulation actions.
At this level, definitions are mainly symbolic, abstract and close to human description.

@@

@@

\subsection{Software}
\label{sec:software}
The library of actions is implemented as an application in the Open Robot Control Software (Orocos) framework \cite{rtt-url,soetens2006}.
The Orocos is a framework to develop real-time robotic and automation applications.
In a typical Orocos application, several components exist which communicate over (possibly real-time) data ports.
The library of actions consists of several components which are shown in fig.\ref{fig:software_structure}.
Some of the components communicate to hardware (Sensors and actuators), while others perform calculations and control the execution of actions.
The components are described in the following:
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/software_structure.pdf}
      \caption{ Block diagram of the software for action library.
      The interconnection of the components are shown as well as the interface to ROS nodes and hardware.
}
      \label{fig:software_structure}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

In this section, we will provide experimental results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Manipulation Action (ManiAc) Dataset}
\label{sec:maniacdataset}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}

The main contribution of our paper is a novel method for automatic semantic decomposition and recognition of long and complex manipulation sequences.

%\newpage  %% needed for single columns
%\clearpage  %% needed for two columns
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
The research leading to these results has received funding from the European Community’s Seventh Framework Programme FP7/2007-2013 (Programme and Theme: ICT-2011.2.1, Cognitive Systems and Robotics) under grant agreement no. 600578, ACAT. 
\end{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{actionlib_journal}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
%%
%% and use \bibitem to create references. Consult the Instructions
%% for authors for reference list style.
%%
%\bibitem{RefJ}
%% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
%% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
%% etc
%\end{thebibliography}
